\input{_settings/setting}

\title{A Dynamic Approach to ImageNet Competition Challenge}
\author{beomjun shin, hunjae jung, youngjin kim}

\newtheorem{qu}{Question}

\begin{document}

\maketitle

% Project title, list of group members, overview of project idea, a short survey of relevant papers, and description of potential data sets for experiments.
\section{overview of project idea}

In this project, we would like to challenge previous ImageNet 2014 competition by using deep learning framework called Caffe. ImageNet 2014 competition is one of the largest and the most challenging computer vision challenge. In this competition, there were 3 problems which are (1) image classification, (2) object detection, and (3) several objects detection. To solve these problems, we would mainly focus on the techniques called Convolutional Neural Network(CNN) for classification, Regions with Convolutional Neural Network(RCNN) for object detection, and several computer vision skills what we?ve learned in class to optimize our algorithm. Caffe, which is deep learning framework, let us use CNN/RCNN easily and provides several API function for deep learning algorithms. When we success on image classification and object detection tasks, we would make simple application to show our works. When the user upload there own picture on the application, the application will provides related images depending on the result of image classification tasks. And based on this project experience, we hope we could challenge on ImageNet 2016 competition or create a novel application by using this state-of-the-art performance.

\section{short survey}

\section{dataset}

\end{document}